### 2016-11-07 paper3.tex
Added short captions for each figure

\subsection{Superbubble Feedback}
\begin{table*}
\input{figures3/z0_table.tex}
\caption{Redshift 0 properties of the full MUGS2 sample.  All masses and
    particle counts are measured within a $R_{\rm vir}$ sphere centred on the halo, except for
$M_{\rm central}$, which is measured within a $0.1\;R_{\rm vir}$ sphere.}
\label{z0_table}
\end{table*}
\begin{figure*}
    \includegraphics[width=\textwidth]{figures3/stellar_edge.eps}
    \includegraphics[width=\textwidth]{figures3/stellar_face.eps}
    \caption{Mock optical stellar observations of each MUGS2 galaxy.  RGB
        channels are calculated using \citet{Marigo2008} stellar populations.
        The top three rows show the galaxies edge on, while the bottom three show the
        galaxies face on.  The galaxies are sorted in order of halo mass, and
        galaxies that overproduce stars are labelled with red.  These images do
    not include the effects of dust extinction}
    \label{stellar_image}
\end{figure*}

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{figures3/column_edge.eps}
    \includegraphics[width=\textwidth]{figures3/column_face.eps}
    \caption{{\sc Hi} column density in each of the MUGS2 galaxies.  As in
    Fig.~\ref{stellar_image}, the top three rows show the galaxy edge on.}
    \label{gas_column}
\end{figure*}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/SMHMR.eps}
    \caption{Stellar mass versus halo mass at $z=0$.  The observed stellar mass to
        halo mass relation is from \citet{Hudson2015}'s weak lensing study of
        galaxies to $z=0.8$.  Galaxies that fall within this range are shown as
        blue squares, while galaxies above the curve (those which form too many
        stars) are shown as red circles.  For comparison, the black stars show
        galaxies from the NIHAO sample \citep{Wang2015}.}
    \label{SMHMR}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/rotcurve.eps}
    \caption{As is clear from the above rotation curves, galaxies which
    overproduce stars (shown in dotted red) also have large central concentrations,
    giving steeply peaked rotation curves inconsistent with those seen in local $L*$
    galaxies.  Galaxies with well-regulated star formation have flat rotation
curves (shown in solid blue).}
    \label{rotation_curve}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/stellar_central.eps}
    \caption{The stellar mass and the central baryonic mass show a tight
        correlation.  For the well-regulated population, roughly $40\%$ of the
        central baryons are stars, while for the unregulated population has
        converted $\sim70\%$ of the central baryon mass into stars.}
    \label{stellar_central}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/phase.eps}
    \caption{Gas phase diagrams for a well-regulated galaxy (g24334) and an
        unregulated galaxy (g19195).  Colour shows the amount of mass at a given
        $\rho-T$ point.  The top phase diagram shows the characteristic slope
        for adiabatic (dashed line) and isobaric (dotted line) processes.  As
        can be seen, both galaxies are qualitatively the same.  Both show the
        equilibrium cooling curve below $10^4\K$, and both show the adiabatic
        evolution of superbubble-heated gas as it leaves the disc.}
    \label{phase}
\end{figure}

@@

\subsection{Time Evolution} 
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/stellar_fraction_time.eps}
    \caption{Stellar mass fraction versus time.  As is clear, for the unregulated
        population the buildup of stellar mass above $\sim3\%$ of the halo mass
        happens very rapidly, often on time-scales of $\sim1\Gyr$.  The runaway
        in the unregulated population stops simply when the disc has been
        sufficiently depleted of gas that little remains to form new stars.}
    \label{stellar_fraction_time}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/SMHMR_time.eps}
    \caption{Stellar mass versus halo mass, as shown in Fig.~\ref{SMHMR}, but
        with trails added to show time evolution.  For halo masses below
        $\sim\rm{a\;few}\times10^{11}$, the evolution of the regulated and
        unregulated populations are indistinguishable.  The grey bar shows the
        $z=0$ SMHMR, as in Fig.~\ref{SMHMR}}
    \label{SMHMR_time}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/stellar_central_time.eps}
    \caption{Stellar mass versus central baryon mass. The stellar mass here can be
    seen to vary much more smoothly over the evolution, without the slight
    `jump' seen in Fig.~\ref{stellar_fraction_time}.}
    \label{stellar_central_time}
\end{figure}

@@

\subsection{Galactic Outflows}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/massloading_time.eps}
    \caption{Outflow mass loading decreases as galaxies grow over time, as
    was previously shown by \citet{Keller2015}.  Here we see, when examining the
    mean mass loadings for the two populations (the well-regulated galaxies,
    where stellar feedback succeeds, and the unregulated galaxies, where it
    fails), that the unregulated galaxies have their mass loadings decrease
    sooner, and to lower values, than the well-regulated population.  The error
bars here are the $1\sigma$ scatter in each population.}
    \label{massloading_time}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/massloading_halo.eps}
    \caption{Unlike in the previous figure, if we look at mass loading as
    a function of halo mass, we instead see no significant difference between
    the two populations.  Instead, both follow a similar trajectory, and the haloes which
    fail to self-regulate do so simply because they reach a higher mass earlier.}
    \label{massloading_halo}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/massloading_central.eps}
    \caption{The mass loadings of the two populations are even more in agreement
    if we look at their relation to the central baryonic mass.  As with the mass
    loading versus halo mass relation, we can fit a broken power law to this relation
    (shown here as the dashed line).}
    \label{massloading_central}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/coldmassloading.eps}
    \caption{Mean outflow mass loading for the full sample, as a function of
    halo mass/virial temperature, and split into cold ($T<10^5\K$) and hot
    ($T>10^5\K$) components.  For low-mass haloes, outflows are dominated by
    relatively cold gas (cooler superbubbles, and entrained material), while heavier
    haloes have primarily hot outflows.  The transition occurs at a halo mass of
    $M_{\rm halo}\sim10^{11}\;\Msun$, or a virial temperature of $6\times10^5\K$.}
    \label{coldmassloading}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/massloading_escape.eps}
    \caption{Mean outflow mass loading for the full sample, as a function of the
        escape velocity on the inner surface of our outflow shell
        ($0.1R_{\rm vir}$).  Each galaxy is sampled 128 times over its evolution,
        giving us 2304 points across a range of redshifts.  As can be seen, at
        $v_{\rm esc}\sim 250\;km/s$, the mass loading begins to fall precipitously.
        This corresponds to the sound speed of solar-metallicity gas at a
        temperature of $3.5\times10^{6}\K$.  This means that for gas at or
        above this temperature, sound waves alone are able to propel material
        significantly above the disc, and that kinetic energy losses due to
        shocks will be minimal.  Gas cooler than that will need to be propelled
        supersonically, and will drive shocks in the CGM.}
    \label{massloading_escape}
\end{figure}

>>>>

\subsection{Superbubble Feedback}
\begin{table*}
\input{figures3/z0_table.tex}
\caption{Redshift 0 properties of the full MUGS2 sample.  All masses and
    particle counts are measured within a $R_{\rm vir}$ sphere centred on the halo, except for
$M_{\rm central}$, which is measured within a $0.1\;R_{\rm vir}$ sphere.}
\label{z0_table}
\end{table*}
\begin{figure*}
    \includegraphics[width=\textwidth]{figures3/stellar_edge.eps}
    \includegraphics[width=\textwidth]{figures3/stellar_face.eps}
    \caption[Mock stellar images of MUGS2 galaxies]{Mock optical stellar
    observations of each MUGS2 galaxy.  RGB channels are calculated using
    \citet{Marigo2008} stellar populations.  The top three rows show the
    galaxies edge on, while the bottom three show the galaxies face on.  The
    galaxies are sorted in order of halo mass, and galaxies that overproduce
    stars are labelled with red.  These images do not include the effects of
    dust extinction}
    \label{stellar_image}
\end{figure*}

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{figures3/column_edge.eps}
    \includegraphics[width=\textwidth]{figures3/column_face.eps}
    \caption[HI column density images for MUGS2 galaxies]{{\sc Hi} column
    density in each of the MUGS2 galaxies.  As in Fig.~\ref{stellar_image}, the
    top three rows show the galaxy edge on.}
    \label{gas_column}
\end{figure*}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/SMHMR.eps}
    \caption[MUGS2 stellar mass to halo mass relation]{Stellar mass versus halo
    mass at $z=0$.  The observed stellar mass to halo mass relation is from
    \citet{Hudson2015}'s weak lensing study of galaxies to $z=0.8$.  Galaxies
    that fall within this range are shown as blue squares, while galaxies above
    the curve (those which form too many stars) are shown as red circles.  For
    comparison, the black stars show galaxies from the NIHAO sample
    \citep{Wang2015}.}
    \label{SMHMR}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/rotcurve.eps}
    \caption[MUGS2 rotation curves]{As is clear from the above rotation curves,
    galaxies which overproduce stars (shown in dotted red) also have large
    central concentrations, giving steeply peaked rotation curves inconsistent
    with those seen in local $L*$ galaxies.  Galaxies with well-regulated star
    formation have flat rotation curves (shown in solid blue).}
    \label{rotation_curve}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/stellar_central.eps}
    \caption[Stellar mass vs. central baryonic mass in MUGS2 galaxies]{The stellar mass and the central baryonic mass show a tight
        correlation.  For the well-regulated population, roughly $40\%$ of the
        central baryons are stars, while for the unregulated population has
        converted $\sim70\%$ of the central baryon mass into stars.}
    \label{stellar_central}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/phase.eps}
    \caption[Gas phase diagram in two MUGS2 galaxies]{Gas phase diagrams for a
    well-regulated galaxy (g24334) and an unregulated galaxy (g19195).  Colour
    shows the amount of mass at a given $\rho-T$ point.  The top phase diagram
    shows the characteristic slope for adiabatic (dashed line) and isobaric
    (dotted line) processes.  As can be seen, both galaxies are qualitatively
    the same.  Both show the equilibrium cooling curve below $10^4\K$, and both
    show the adiabatic evolution of superbubble-heated gas as it leaves the
    disc.}
    \label{phase}
\end{figure}

@@

\subsection{Time Evolution} 
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/stellar_fraction_time.eps}
    \caption[Stellar mass fraction evolution in MUGS2]{Stellar mass fraction
    versus time.  As is clear, for the unregulated population the buildup of
    stellar mass above $\sim3\%$ of the halo mass happens very rapidly, often on
    time-scales of $\sim1\Gyr$.  The runaway in the unregulated population stops
    simply when the disc has been sufficiently depleted of gas that little
    remains to form new stars.}
    \label{stellar_fraction_time}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/SMHMR_time.eps}
    \caption[Stellar mass vs. halo mass evolution in MUGS2]{Stellar mass versus
    halo mass, as shown in Fig.~\ref{SMHMR}, but with trails added to show time
    evolution.  For halo masses below $\sim\rm{a\;few}\times10^{11}$, the
    evolution of the regulated and unregulated populations are
    indistinguishable.  The grey bar shows the $z=0$ SMHMR, as in
    Fig.~\ref{SMHMR}}
    \label{SMHMR_time}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/stellar_central_time.eps}
    \caption[Stellar mass vs. central baryonic mass evolution in MUGS2]{Stellar
    mass versus central baryon mass. The stellar mass here can be seen to vary
    much more smoothly over the evolution, without the slight `jump' seen in
    Fig.~\ref{stellar_fraction_time}.}
    \label{stellar_central_time}
\end{figure}

@@

\subsection{Galactic Outflows}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/massloading_time.eps}
    \caption[Outflow mass loading evolution in MUGS2]{Outflow mass loading
    decreases as galaxies grow over time, as was previously shown by
    \citet{Keller2015}.  Here we see, when examining the mean mass loadings for
    the two populations (the well-regulated galaxies, where stellar feedback
    succeeds, and the unregulated galaxies, where it fails), that the
    unregulated galaxies have their mass loadings decrease sooner, and to lower
    values, than the well-regulated population.  The error bars here are the
    $1\sigma$ scatter in each population.}
    \label{massloading_time}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/massloading_halo.eps}
    \caption[Mass loading as a function of halo mass in MUGS2]{Unlike in the
    previous figure, if we look at mass loading as a function of halo mass, we
    instead see no significant difference between the two populations.  Instead,
    both follow a similar trajectory, and the haloes which fail to self-regulate
    do so simply because they reach a higher mass earlier.}
    \label{massloading_halo}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/massloading_central.eps}
    \caption[Mass loadings as a function of disc mass]{The mass loadings of the two populations are even more in agreement
    if we look at their relation to the central baryonic mass.  As with the mass
    loading versus halo mass relation, we can fit a broken power law to this relation
    (shown here as the dashed line).}
    \label{massloading_central}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/coldmassloading.eps}
    \caption[Outflow mass loading for cold and hot gas]{Mean outflow mass loading for the full sample, as a function of
    halo mass/virial temperature, and split into cold ($T<10^5\K$) and hot
    ($T>10^5\K$) components.  For low-mass haloes, outflows are dominated by
    relatively cold gas (cooler superbubbles, and entrained material), while heavier
    haloes have primarily hot outflows.  The transition occurs at a halo mass of
    $M_{\rm halo}\sim10^{11}\;\Msun$, or a virial temperature of $6\times10^5\K$.}
    \label{coldmassloading}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures3/massloading_escape.eps}
    \caption[Mass loading vs. escape velocity of disc]{Mean outflow mass loading for the full sample, as a function of the
        escape velocity on the inner surface of our outflow shell
        ($0.1R_{\rm vir}$).  Each galaxy is sampled 128 times over its evolution,
        giving us 2304 points across a range of redshifts.  As can be seen, at
        $v_{\rm esc}\sim 250\;km/s$, the mass loading begins to fall precipitously.
        This corresponds to the sound speed of solar-metallicity gas at a
        temperature of $3.5\times10^{6}\K$.  This means that for gas at or
        above this temperature, sound waves alone are able to propel material
        significantly above the disc, and that kinetic energy losses due to
        shocks will be minimal.  Gas cooler than that will need to be propelled
        supersonically, and will drive shocks in the CGM.}
    \label{massloading_escape}
\end{figure}

### 2016-11-07 paper4.tex
Added short captions for each figure

\begin{figure}
    \includegraphics[width=0.5\textwidth]{figures4/SPARC_plot.eps}
    \caption{Total acceleration ($g_{obs}$) vs acceleration due to baryons
    ($g_{bar}$) from 1800 data points in the $z=0$ MUGS2 sample, shown in the
    blue 2-dimensional histogram.  The dotted black curve shows the 1:1 relation
    expected if the acceleration was due to baryons alone (without dark matter),
    while the solid line shows the relation presented in \citet{McGaugh2016}.
    A Gaussian distribution fitted to these residuals finds a
    variance of $\sigma=0.05$ dex, significantly lower than the 0.11 dex found
    by \citet{McGaugh2016}.} \label{SPARC_plot}
\end{figure}
\begin{figure}
    \includegraphics[width=0.5\textwidth]{figures4/redshift_evolution.eps}
    \caption{The  simulated $g_{obs}-g_{bar}$ relation is not constant with
    redshift.  As this figure shows, at higher redshift the low $g_{bar}$ slope
    is much shallower than at $z=0$.  This shows that for high redshift
    galaxies, their discs can be depleted of baryons compared with $z=0$.  We
    have focused on the low $g_{bar}$ end of the relation here, where the
    changes are most significant.}
    \label{redshift_evolution}
\end{figure}
\begin{figure}
    \includegraphics[width=0.5\textwidth]{figures4/FB_effects.eps}
    \caption{The evolution seen in figure~\ref{redshift_evolution} is primarily
    driven by feedback.  This can be seen when looking at the same galaxy with
    and without feedback.  Without feedback, the baryon fraction within the disc
    increases slightly from $z=0$ to $z=2$, but still roughly follows the SPARC
    relation.  At $z=2$, strong outflows in the galaxy expel most of the baryons
    from the disc, flattening the acceleration relation.  This effect is
    sensitive to the frequent merger-driven starbursts at high redshift, which
    can drive bursty outflows.}
    \label{FB_effects}
\end{figure}
\section{Results}
\subsection{z=0 Acceleration Relation}
The MUGS2 sample gives us 1800 acceleration data points, just over 2/3 the
sample size of \citet{McGaugh2016}. We show in figure~\ref{SPARC_plot} the
$g_{obs}-g_{bar}$ relation for the MUGS2 sample, compared both to the pure
baryonic acceleration and the SPARC acceleration relation.  It is clear these
simulated galaxies follow the \citet{McGaugh2016} relation {\it extremely} well.
As can be seen from the inset residual distribution, our simulated galaxies
follow the SPARC relation even more tightly than the actual observational data.
The scatter we do see, with $\sigma=0.05$ dex, is consistent with the
\citet{McGaugh2016} estimates.  They decomposed their scatter of $0.11$
dex into different sources, and when all of the observational uncertainties are
removed, the remaining intrinsic scatter gives a variance of $\sigma=0.06$ dex,
very close to the value we find here.  A reduced $\chi^2$ statistic of the SPARC
relation fit to the $z=0$ MUGS2 data finds a very good fit, with $\chi^2_\nu =
1.25$.  These simulation data are fit by equation~\ref{g_fit} at least as well
as the original SPARC data.

>>>>

\begin{figure}
    \includegraphics[width=0.5\textwidth]{figures4/SPARC_plot.eps}
    \caption[Total acceleration vs. baryonic acceleration in MUGS2]{Total
    acceleration ($g_{obs}$) vs acceleration due to baryons ($g_{bar}$) from
    1800 data points in the $z=0$ MUGS2 sample, shown in the blue 2-dimensional
    histogram.  The dotted black curve shows the 1:1 relation expected if the
    acceleration was due to baryons alone (without dark matter), while the solid
    line shows the relation presented in \citet{McGaugh2016}.  A Gaussian
    distribution fitted to these residuals finds a variance of $\sigma=0.05$
    dex, significantly lower than the 0.11 dex found by \citet{McGaugh2016}.}
    \label{SPARC_plot}
\end{figure}
\begin{figure}
    \includegraphics[width=0.5\textwidth]{figures4/redshift_evolution.eps}
    \caption[Redshift evolution of acceleration relation]{The  simulated
    $g_{obs}-g_{bar}$ relation is not constant with redshift.  As this figure
    shows, at higher redshift the low $g_{bar}$ slope is much shallower than at
    $z=0$.  This shows that for high redshift galaxies, their discs can be
    depleted of baryons compared with $z=0$.  We have focused on the low
    $g_{bar}$ end of the relation here, where the changes are most significant.}
    \label{redshift_evolution}
\end{figure}
\begin{figure}
    \includegraphics[width=0.5\textwidth]{figures4/FB_effects.eps}
    \caption[Feedback effects on acceleration relation]{The evolution seen in
    figure~\ref{redshift_evolution} is primarily driven by feedback.  This can
    be seen when looking at the same galaxy with and without feedback.  Without
    feedback, the baryon fraction within the disc increases slightly from $z=0$
    to $z=2$, but still roughly follows the SPARC relation.  At $z=2$, strong
    outflows in the galaxy expel most of the baryons from the disc, flattening
    the acceleration relation.  This effect is sensitive to the frequent
    merger-driven starbursts at high redshift, which can drive bursty outflows.}
    \label{FB_effects}
\end{figure}
\section{Results}
\subsection{z=0 Acceleration Relation}
The MUGS2 sample gives us 1800 acceleration data points, just over 2/3 the
sample size of \citet{McGaugh2016}. We show in figure~\ref{SPARC_plot} the
$g_{obs}-g_{bar}$ relation for the MUGS2 sample, compared both to the pure
baryonic acceleration and the SPARC acceleration relation.  It is clear these
simulated galaxies follow the \citet{McGaugh2016} relation {\it extremely} well.
As can be seen from the inset residual distribution, our simulated galaxies
follow the SPARC relation even more tightly than the actual observational data.
The scatter we do see, with $\sigma=0.05$ dex, is consistent with the
\citet{McGaugh2016} estimates.  They decomposed their scatter of $0.11$
dex into different sources, and when all of the observational uncertainties are
removed, the remaining intrinsic scatter gives a variance of $\sigma=0.06$ dex,
very close to the value we find here.  A reduced $\chi^2$ statistic of the SPARC
relation fit to the $z=0$ MUGS2 data finds a very good fit, with $\chi^2_\nu =
1.25$.  These simulation data are fit by equation~\ref{g_fit} at least as well
as the original SPARC data.
